\documentclass[12pt]{article}
\setlength{\headheight}{0ex}
\setlength{\headsep}{0ex}
\input{hogg_nasa}
\pagestyle{empty}

\begin{document}

\subsection*{Budget justification}

\paragraph{Senior personnel:}
Funds are allocated for 0.5 month per year of the PI's salary.
The PI will be responsible for scientific oversight of the project,
supervising the completion of scientific papers and delivery of
\catalogname\ to the community.

\paragraph{Personnel:}
Funds are requested for a full-time postdoctoral scholar, who will
execute the scientific program.
This includes running, modifying, and publishing the software used;
creating, vetting, and delivering \catalogname;
and performing and publishing the population inferences.

\paragraph{Equipment:}
Funds are requested for a modest laptop computer (11-inch MacBook Air
or equivalent) for the PI and the postdoctoral scholar in Year~1 only.

\paragraph{Travel:}
Travel funding is estimated on three collaboration group-meeting trips
per year for all three of the personnel, and one trip per year for all
three of the personnel to the American Astronomical Society Winter
Meeting.

\paragraph{Publications:}
Funds are allocated for about 20 pages of ApJ or AJ page charges per
year, plus contingency for poster-making or other publication-related
supplies.

\paragraph{Code and data preservation services:}
We did not allocate any funding to long-term code storage and
preservation.
We have good experience both with NYU ITS and the company
\project{github} for long-term storage and maintenance of code,
including revision histories, at no direct cost to the research
projects.
Similarly, we have had good experience with NYU ITS and the
NASA-funded data archives for long-term storage and preservation
of research data, including value-added high-level data products
like those produced in this project, again at no direct cost to
the projects.

\end{document}
